Describing the scale and composition of calls for police service: a replication and extension using open data

### 2022-02-10 paper.Rmd
Edited until Results section

The data used for this study covers the city of Detroit in Michigan, US. The City of Detroit authority publish 911 emergency calls for service data through their Open Data Portal.^[Accessible via https://data.detroitmi.gov/.] In alignment with @ratcliffe2021policing the data used here is subset for the year 2019 and excludes those calls initiated by an officer in order to capture public-initiated calls. Each individual incident has a corresponding timestamp and location coordinates to define the call in time and space.

For each incident, the police response time and time on the scene are reported. In sum, these comprise the total deployed time officers spend on the incident. Calls which had a _total deployed time_ (response time + time on scene) or _time on scene_ of zero minutes, negative values or missing were excluded. The data permits a distinction between the time spent resolving incidents with and without the response time. As noted, @lum2021can considered the _time on scene_ measure to be preferable. Here, for completeness, both measurements are reported.

@@

A series of descriptive statistics summarize the time consumed by each demand type. As an aggregate measure, we report the sum time spent on each demand classification by the number of officer shifts.^[Consistent with Ratcliffe (2021) a shift is defined as 7.5 hours. The sum total of hours for each demand classification over the year is divided by 7.5.] For comprehensiveness and transparency, we also report the mean, median, standard deviation, range, and in the Appendix, a histogram of the underlying distribution in minutes. This sheds on light on how long a 'typical' call might take while noting a probable skew in the distribution. Such a skew would suggest that averages of time [e.g., @lum2021can] or aggregate measures of time [e.g., @ratcliffe2021policing] in isolation are insufficient and potentially mask important underlying variation, namely, that a small number of high-demand calls drag up the mean and inflate aggregate measures of time. To investigate this distribution, we plot Lorenz curves for each demand classification. Lorenz curves plot the cumulative distribution of a variable (in this case, time on scene) against the cumulative distribution of a unit (in this case, calls) [@bernasco2017more]. By way of example, we report on these figures according to arbitrary thresholds of 25% and 50%. This sheds light on the degree to which a disproportionately large amount of officer time might be consumed by just a small number of calls.

>>>>

The data used for this study cover the city of Detroit in Michigan, US. The City of Detroit authority publish 911 emergency calls for service data through their Open Data Portal.^[Accessible via https://data.detroitmi.gov/.] In alignment with @ratcliffe2021policing, the data used here are subset for the year 2019 and exclude those calls initiated by an officer in order to capture public-initiated calls. Each individual incident has a corresponding timestamp and location coordinates to define the call in time and space.

For each incident, the police response time and time on the scene are reported. In sum, these comprise the total deployed time officers spend on the incident. Calls which had a _total deployed time_ (response time + time on scene) or _time on scene_ of zero minutes, negative values or missing were excluded. The data permit a distinction between the time spent resolving incidents with and without the response time. As noted, @lum2021can considered the _time on scene_ measure to be preferable. Here, for completeness, both measurements are reported.

@@

A series of descriptive statistics summarize the time consumed by each demand type. As an aggregate measure, we report the sum time spent on each demand classification by the number of officer shifts.^[Consistent with Ratcliffe (2021) a shift is defined as 7.5 hours. The sum total of hours for each demand classification over the year is divided by 7.5.] For comprehensiveness and transparency, we also report the mean, median, standard deviation, and range in the Appendix, next to a histogram of the underlying distribution in minutes. This sheds on light on how long a 'typical' call might take while noting a probable skew in the distribution. Such a skew would suggest that averages of time [e.g., @lum2021can] or aggregate measures of time [e.g., @ratcliffe2021policing] in isolation are insufficient and potentially mask important underlying variation, namely, that a small number of high-demand calls drag up the mean and inflate aggregate measures of time. To investigate this distribution, we plot Lorenz curves for each demand classification. Lorenz curves plot the cumulative distribution of a variable (in this case, time on scene) against the cumulative distribution of a unit (in this case, calls) [@bernasco2017more]. By way of example, we report on these figures according to arbitrary thresholds of 25% and 50% of time spent. This sheds light on the degree to which a disproportionately large amount of officer time might be consumed by just a small number of calls.
